---
title: "Untitled"
author: "Tie Ma"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
#Note: this file include the processing of downloding the Data from the IMS and cleaning process 
#wrote by Tie at 2024/05/18
```

```{R}
#update history
################
#2024/05/24  #0.0.1 create the this marketdown and doing the first round of test data collection. 
#2024/05/25  #0.0.2 further improve the data cleaning 
#2024/05/26  #0.0.3 add the code section of create IMF data check list for better understand and cleaning this data.  
################

```



```{r setup, include=FALSE}
#this file is for processing the Raw data from entire OECD data set from 1950 - 2023 
#as the Raw code processing file for the RA data job for professor Hassmant
#Tie Ma 2024/05/18

################################################################################

#clean the enviroment
rm(list = ls())

#set the working direction
#for mac
#setwd("/Users/tie/Documents/GitHub/RA-data-clening")

#for windosw
#setwd("D:/github/RA-data-clening/code")



################################################################################
#Step one Lode the all package that necessary. 
#some of them may not be used this file
#I just copy them around, so it will make my life easier 

library (lubridate)     #the time series processing package
library (cansim)        #provides easy access to the statistics canada data tale
library (WDI)           #Accesses data from the world development indicators
library (fredr)         #provide an interface to the federal reserve economic data API
library (tsbox)         #Make time series convverstion, aggregation and plotting simple
library (RColorBrewer)  #color palettes for R graphics
library(wesanderson)    #Provides color palettes inspired by Wes Anderson films.
library(writexl)        #Writes data frames to Excel files.
library(tidyr)          #Tidies messy data   
library(xts)            #Extensible time series class for R   
library(dplyr)          #Data manipulation and transformation.
library(openxlsx)       #Read, write, and edit Excel files.
library(IMFData)     #accessing the data from the IMF data 

```

```{R}
################################################################################
#this section of the code does no  work
#imf_databases <- DataStructureMethod("IMF")
#print(imf_databases)
################################################################################
```

```{R}
#check the available data base ID
#availableDB <- DataflowMethod()
#availableDB$DatabaseID
```


```{r}

# Set databaseID and other parameters
#accessing the data from the IFS
IFS.available.codes <- DataStructureMethod("IFS")


# Available dimension code
names(IFS.available.codes)

#check the name
IFS.available.codes[[1]]

#find all the avaiable indicator for the GDP
Indicator_names <- CodeSearch(IFS.available.codes, "CL_INDICATOR_IFS", "NGDP")
head(Indicator_names, n = 10)


#check the availabel region name
evil <- IFS.available.codes$CL_AREA_IFS
print(evil)

#create a new place for the saving the IMF data
dir.create("D:\\github\\RA-data-clening\\Data\\IFS_data", recursive = TRUE)

# save the IFS coutries check list 
write.csv(evil, "D:\\github\\RA-data-clening\\Data\\IFS_data\\IFS_country_check_list.csv")



```


```{r}

# 定义函数以获取并存储特定国家和指标的数据
databaseID <- "IFS"
startdate <- "1950-01-01"
enddate <- "2023-12-31"
checkquery <- FALSE

# 列出要测试的指标
indicators <- c(
  "NGDP_XDC",      # Gross Domestic Product, Nominal, Domestic Currency
  "NGDP_R_XDC"     # Gross Domestic Product, Real, Domestic Currency
)

# 完整的国家代码列表
country_codes <- c(
  "AF", "AL", "DZ", "AD", "AO", "AI", "AG", "5M", "AR", "AM", "AW", "AU", "AT", "AZ", "BS", "BH", "BD", "5W",
  "5B", "BB", "BY", "BE", "R1", "BZ", "BJ", "BM", "BT", "BO", "BA", "BW", "BR", "BN", "BG", "BF", "BI", "CV",
  "KH", "CM", "CA", "KY", "CF", "1C_752", "TD", "CL", "HK", "MO", "CN", "CO", "KM", "CD", "CG", "CR", "CI",
  "HR", "CU", "1C_355", "CW", "CY", "CZ", "CSH", "DK", "DJ", "DM", "DO", "5I", "DE2", "EC", "EG", "SV", "GQ",
  "ER", "EE", "SZ", "ET", "U2", "4F", "FO", "FJ", "FI", "FR", "PF", "GA", "GM", "GE", "DE", "GH", "GI", "GR",
  "GL", "GD", "GP", "GU", "GT", "GG", "GF", "GN", "GW", "GY", "HT", "HN", "HU", "IS", "IN", "ID", "1E", "X0",
  "IR", "IQ", "IE", "7B", "IM", "IL", "IT", "JM", "JP", "JE", "JO", "KZ", "KE", "KI", "KR", "XK", "KW", "KG",
  "LA", "LV", "LB", "LS", "LR", "LY", "LT", "LU", "MG", "MW", "MY", "MV", "ML", "MT", "MH", "MQ", "MR", "MU",
  "MX", "FM", "MD", "MN", "ME", "MS", "MA", "MZ", "MM", "NA", "NR", "NP", "AN", "NL", "NC", "NZ", "NI", "NE",
  "NG", "MK", "NO", "OM", "PK", "PW", "PA", "PG", "PY", "PE", "PH", "PL", "PT", "QA", "RE", "RO", "RU", "RW",
  "PM", "WS", "SM", "ST", "SA", "SN", "RS", "SC", "SL", "SG", "SX", "SK", "SI", "SB", "SO", "ZA", "SS", "ES",
  "LK", "KN", "LC", "VC", "SD", "SR", "SE", "CH", "SY", "TW", "TJ", "TZ", "TH", "TL", "TG", "TO", "TT", "TN",
  "TR", "TM", "TC", "TV", "UG", "UA", "AE", "GB", "US", "UY", "SUH", "UZ", "VU", "VE", "VN", "PS", "1C_473",
  "1C_459", "YE", "YUC", "ZM", "ZW", "XR29", "M49_002", "1C_ALLC", "1C_ALL", "W0", "1C_All_Countries_Published",
  "1C_ALLG", "M49_019", "M49_142", "5O", "5X", "Countries_Home_Portal_Presentation", "F3", "5Y", "XS25", "XR43",
  "1C_903", "1C_994", "1C_EMU", "M49_150", "120", "119", "1C_Middle_East_and_Central_Asia", "1C_NANSA", "1C_NASA",
  "1C_NSC", "M49_009", "1C_970", "1C_SRF_less_EMU", "1C_SRF_plus_EMU", "1C_SRF", "F6", "7A", "WAEMU", "A10",
  "W00"
)
# 对应的国家名称列表
country_names <- c(
  "Afghanistan", "Albania", "Algeria", "Andorra", "Angola", "Anguilla", "Antigua and Barbuda", "Arab Monetary Fund", 
  "Argentina", "Armenia", "Aruba", "Australia", "Austria", "Azerbaijan", "Bahamas", "Bahrain", "Bangladesh", 
  "Banque des Etats de l'Afrique Centrale", "Bank for International Settlements", "Barbados", "Belarus", "Belgium", 
  "Belgo-Luxembourg Economic Union", "Belize", "Benin", "Bermuda", "Bhutan", "Bolivia", "Bosnia and Herzegovina", 
  "Botswana", "Brazil", "Brunei Darussalam", "Bulgaria", "Burkina Faso", "Burundi", "Cabo Verde", "Cambodia", 
  "Cameroon", "Canada", "Cayman Islands", "Central African Republic", "Central Bank West Africa", "Chad", "Chile", 
  "Hong Kong, China", "Macao", "China", "Colombia", "Comoros", "Congo, the Democratic Republic of the", "Congo", 
  "Costa Rica", "Cote d'Ivoire", "Croatia", "Cuba", "Curacao & St. Maarten", "Curacao", "Cyprus", "Czech Republic", 
  "Former Czechoslovakia", "Denmark", "Djibouti", "Dominica", "Dominican Republic", "Eastern Caribbean Central Bank", 
  "East Germany", "Ecuador", "Egypt", "El Salvador", "Equatorial Guinea", "Eritrea", "Estonia", "Eswatini", 
  "Ethiopia", "Euro area", "European Central Bank", "Faroe Islands", "Fiji", "Finland", "France", "French Polynesia", 
  "Gabon", "Gambia", "Georgia", "Germany", "Ghana", "Gibraltar", "Greece", "Greenland", "Grenada", "Guadeloupe", 
  "Guam", "Guatemala", "Guernsey", "French Guiana", "Guinea", "Guinea-Bissau", "Guyana", "Haiti", "Honduras", 
  "Hungary", "Iceland", "India", "Indonesia", "International Bank for Reconstruction and Development", 
  "IMF Member Countries", "Iran", "Iraq", "Ireland", "Islamic Development Bank", "Isle of Man", "Israel", "Italy", 
  "Jamaica", "Japan", "Jersey", "Jordan", "Kazakhstan", "Kenya", "Kiribati", "Korea, Republic of", "Kosovo, Republic of", 
  "Kuwait", "Kyrgyzstan", "Lao People's Democratic Republic", "Latvia", "Lebanon", "Lesotho", "Liberia", "Libya", 
  "Lithuania", "Luxembourg", "Madagascar", "Malawi", "Malaysia", "Maldives", "Mali", "Malta", "Marshall islands", 
  "Martinique", "Mauritania", "Mauritius", "Mexico", "Micronesia, Federated States of", "Moldova, Republic of", 
  "Mongolia", "Montenegro", "Montserrat", "Morocco", "Mozambique", "Myanmar", "Namibia", "Nauru", "Nepal", 
  "Netherlands Antilles", "Netherlands", "New Caledonia", "New Zealand", "Nicaragua", "Niger", "Nigeria", 
  "North Macedonia, Republic of", "Norway", "Oman", "Pakistan", "Palau", "Panama", "Papua New Guinea", "Paraguay", 
  "Peru", "Philippines", "Poland", "Portugal", "Qatar", "Reunion", "Romania", "Russian Federation", "Rwanda", 
  "Saint Pierre and Miquelon", "Samoa", "San Marino", "Sao Tome and Principe", "Saudi Arabia", "Senegal", "Serbia", 
  "Seychelles", "Sierra Leone", "Singapore", "Sint Maarten (Dutch part)", "Slovakia", "Slovenia", "Solomon Islands", 
  "Somalia", "South Africa", "South Sudan", "Spain", "Sri Lanka", "Saint Kitts and Nevis", "Saint Lucia", 
  "Saint Vincent and the Grenadines", "Sudan", "Suriname", "Sweden", "Switzerland", "Syrian Arab Republic", 
  "Taiwan, Province of China", "Tajikistan", "Tanzania, United Republic of", "Thailand", "Timor-Leste", "Togo", 
  "Tonga", "Trinidad and Tobago", "Tunisia", "Turkey", "Turkmenistan", "Turks and Caicos Islands", "Tuvalu", 
  "Uganda", "Ukraine", "United Arab Emirates", "United Kingdom", "United States", "Uruguay", "Former U.S.S.R.", 
  "Uzbekistan", "Vanuatu", "Venezuela, Bolivarian Republic", "Viet Nam", "Palestine, State of", "Yemen Arab Rep.", 
  "Yemen, P.D. Rep.", "Yemen", "Former Yugoslavia", "Zambia", "Zimbabwe", "Advanced Economies", "Africa", 
  "All Countries", "All Countries and Country Groups", "World", "All Countries Published", "All Country Groups", 
  "Americas", "Asia", "BCEAO (Banque Centrale des Etats de l'Afrique de l'Ouest)", "CEMAC", 
  "Countries Home Portal Presentation", "Eastern Africa", "Eastern Caribbean Currency Union", "Developing Asia", 
  "Emerging and Developing Countries", "Emerging and Developing Europe", "EPU/EF", "EMU", "Europe", "G20", "G7", 
  "Middle East and Central Asia", "National Accounts (NSA) Countries", "National Accounts (SA) Countries", 
  "Non SRF countries", "Oceania", "Other Holders", "SRF (excluding EA)", "SRF (including EA)", "SRF Countries", 
  "Sub-Saharan Africa", "WAEMU (West African Economic and Monetary Union)", "Western Hemisphere", 
  "All Countries, excluding the IO"
)

# 初始化一个空的数据框以存储结果
results <- data.frame(
  TimePeriod = character(),
  CountryName = character(),
  stringsAsFactors = FALSE
)

# 定义函数以获取并存储特定国家和指标的数据，并在出现错误时重试
fetch_data <- function(country_code, country_name, indicator) {
  queryfilter <- list(
    CL_FREA = "A",  # 年度数据
    CL_AREA_IFS = country_code,  # 当前国家代码
    CL_INDICATOR_IFS = indicator  # 当前指标
  )
  
  attempt <- 1
  max_attempts <- 3
  success <- FALSE
  no_data_available <- FALSE
  result <- data.frame(TimePeriod = character(), CountryCode = character(), CountryName = character(), Indicator = character(), ObsValue = numeric())
  
  while (attempt <= max_attempts && !success && !no_data_available) {
    tryCatch({
      data <- CompactDataMethod(databaseID, queryfilter, startdate, enddate, checkquery)
      
      if (length(data$Obs) > 0) {
        observations <- data$Obs[[1]]
        if (nrow(observations) > 0) {
          result <- data.frame(
            TimePeriod = observations$`@TIME_PERIOD`,
            CountryCode = country_code,
            CountryName = country_name,
            Indicator = indicator,
            ObsValue = as.numeric(observations$`@OBS_VALUE`)
          )
          success <- TRUE
        }
      } else {
        no_data_available <- TRUE
      }
    }, error = function(e) {
      if (grepl("No data available", e$message)) {
        no_data_available <- TRUE
        message(paste("No data available for", country_code, indicator, ":", e$message))
      } else {
        message(paste("Error fetching data for", country_code, indicator, "on attempt", attempt, ":", e$message))
        attempt <- attempt + 1
        if (attempt <= max_attempts) {
          retry_sleep_time <- runif(1, min = 2, max = 5)
          cat("Retrying in", retry_sleep_time, "seconds...\n")
          Sys.sleep(retry_sleep_time)
        } else {
          message(paste("Failed to fetch data for", country_code, indicator, "after", max_attempts, "attempts. Marking as error."))
        }
      }
    })
  }
  
  return(result)
}

# 分批下载数据
batch_size <- 10
total_countries <- length(country_codes)

for (batch_start in seq(1, total_countries, by = batch_size)) {
  batch_end <- min(batch_start + batch_size - 1, total_countries)
  cat("Processing countries from", batch_start, "to", batch_end, "\n")
  
  for (i in batch_start:batch_end) {
    country_code <- country_codes[i]
    country_name <- country_names[i]
    random_sleep_time <- runif(1, min = 0.1, max = 2.0)
    cat("Sleeping for", random_sleep_time, "seconds...\n")
    
    for (indicator in indicators) {
      result <- fetch_data(country_code, country_name, indicator)
      results <- rbind(results, result)
      Sys.sleep(random_sleep_time)
    }
  }
  
  # 在每批之间添加较长的随机睡眠时间
  random_batch_sleep_time <- runif(1, min = 3.0, max = 5.0)
  cat("Batch completed. Sleeping for", random_batch_sleep_time, "seconds before starting the next batch...\n")
  Sys.sleep(random_batch_sleep_time)
}


```


```{r}

# 将结果数据透视到每个指标一个列
raw_data <- results %>%
  pivot_wider(names_from = Indicator, values_from = ObsValue)

# 查看结果
print(raw_data)

```

```{r}
#raw_data <- results_pivot
#this code is to save in the windows
#write.csv(results_pivot, "D:\\github\\RA-data-clening\\Data\\IFS_data\\IFS_raw_data.csv")

#this line of code is for the mac
write.csv(raw_data, "/Users/tie/Documents/GitHub/RA-data-clening/Data/IFS_data/IFS_raw_data_time_cycle.csv")

#check the total number of countries
#198
n_distinct(raw_data$CountryName)


```


```{r}
#check the data
#unique_values <- raw_data %>% 
  #summarise_all(~ list(unique(.)))
`
```


```{r}
#rename the code so I can use the old code again 


#check the name of the name so i can recycle my code here 
raw_data<- raw_data %>% 
  rename(
  nominal_GDP = NGDP_XDC,
  real_GDP = NGDP_R_XDC,
  REF_AREA = CountryName,
  TIME_PERIOD = TimePeriod)


#double check the number of countries 
n_distinct(raw_data$REF_AREA)
#still got the 198 countries

#check the data
head(raw_data, n = 10)
#the data seem correct.

#the following code is to select the col from the orignal data.
#Selection the data from the raw data
#selection_data <- select(results_pivot, TIME_PERIOD, REF_AREA, nominal_GDP, real_GDP)

```


```{R}

#check the structure of the number of the data
str(raw_data$real_GDP)
#ok its the the number so the following code has been commented out

# Convert observations from character to numeric
#selection_data$ObsValue <- as.numeric(selection_data$ObsValue)
#its already the the num

#change the name to make my life easier 
selection_data <- raw_data

#now, its the time to deal with the date
# Ensure TIME_PERIOD is numeric in the selection_data
selection_data$TIME_PERIOD <- as.numeric(selection_data$TIME_PERIOD)

# Define a complete range of years and countries
all_countries <- unique(selection_data$REF_AREA)

#create the sequence for from the smallest year to the largest year
all_years <- seq(min(selection_data$TIME_PERIOD, na.rm = TRUE), max(selection_data$TIME_PERIOD, na.rm = TRUE), by = 1)

#check the country list and year list 
n_distinct(all_countries)
#ok, still 198 countries 
print(all_years)
#ok, its from the 1950 to the 2023!


# Create a full grid of TIME_PERIOD, REF_AREA, MEASURE, and UNIT_MEASURE
# Assuming all_years and all_countries are defined and unique
#all_years <- c(2021, 2022)  # Example values
#all_countries <- c("USA", "CAN")  # Example values

 #Create full gridfull_grid <- 
  # expand.grid(TIME_PERIOD = all_years, 
               #REF_AREA = all_countries,  
               #nominal_GDP = unique(selection_data$nominal_GDP) 
               #real_GDP = unique(selection_data$real_GDP) )
```


```{r}
#put the time and refrenece together
full_grid <- expand.grid(
  TIME_PERIOD = all_years,
  REF_AREA = all_countries
)

#check the data
#n_distinct(full_grid$REF_AREA)
#countries number 198
#print(min(full_grid$TIME_PERIOD, na.rm = TRUE))
#print(max(full_grid$TIME_PERIOD, na.rm = TRUE))
#print(unique(full_grid$TIME_PERIOD))

#The data is good and as its should be! 
```



```{r}
# put all the data togehter
full_data <- full_grid %>%
  left_join(selection_data, by = c("TIME_PERIOD", "REF_AREA"))

######
#code check
#n_distinct(full_data$REF_AREA) #198 coountires
#n_distinct(full_data$TIME_PERIOD) #1950 - 2023
#unique(full_data$TIME_PERIOD) #1950 - 2023
# the code is working as i expected

#######
# Print the resulting data frame to verify the join
#print(selection_data)

#pivot_wide the data 
#wide_data <- selection_data %>%
  #pivot_wider(
    #names_from = c(PRICE_BASE),
    #values_from = ObsValue,
    #names_sep = "_"
  #)
```



```{r}
#check the entire year check list 
years_count_total <- selection_data %>%
  group_by(REF_AREA) %>%
  summarize(years_of_data = n_distinct(TIME_PERIOD))

#check the number of countries
n_distinct(years_count_total$REF_AREA)

#check the the number of countries have at least one nominal_GDP
years_count_nominal_GDP <- selection_data %>%
  filter(!is.na(nominal_GDP)) %>%
  group_by(REF_AREA) %>%
  summarize(years_of_data = n_distinct(TIME_PERIOD))

#check the number of countries
n_distinct(years_count_nominal_GDP$REF_AREA)
#198

#check the the number of countries have at least one real_GDP
years_count_real_GDP <- selection_data %>%
  filter(is.na(real_GDP))  %>%
  group_by(REF_AREA) %>%
  summarize(years_of_data = n_distinct(TIME_PERIOD))
n_distinct(years_count_real_GDP$REF_AREA)
#185
#which countries have 0 in the real GDP 


# Count the number of years for each country with non-NA values for both L and LR
years_count <- selection_data %>%
  filter(!is.na(nominal_GDP) & !is.na(real_GDP)) %>%
  group_by(REF_AREA) %>%
  summarize(years_of_data = n_distinct(TIME_PERIOD))



n_distinct(years_count$REF_AREA)

#only 185 countries have both

```
```

# Filter countries with at least 25 years of data


```{r}
#country that be keep
countries_to_keep <- years_count %>%
  filter(years_of_data >= 25) %>%
  pull(REF_AREA)
  
#check how many countries to keep
n_distinct(countries_to_keep)
#only to keep 104 countries
```




```{r}
#country that be delete
countries_to_delete <- years_count %>%
  filter(years_of_data < 25) %>%
  pull(REF_AREA)
  
n_distinct(countries_to_delete)
#81 countries need to be delete
```



# Filter the original test_data to keep only the selected countries


```{r}

filtered_data <- selection_data  %>%
  filter(REF_AREA %in% countries_to_keep)


```



```{r}
complete_filtered_data <- filtered_data %>%
  group_by(REF_AREA) %>%
  complete(TIME_PERIOD = 1950:2023) %>%
  ungroup()

```



# Check if every country has data for the entire time period from 1950 to 2023

```{r}
coverage_check <- complete_filtered_data %>%
  group_by(REF_AREA) %>%
  summarize(complete_years = all(1950:2023 %in% TIME_PERIOD), .groups = 'drop')
```

```{r}
# Print the coverage check
print(coverage_check, n = 100)
```


```{r}

# the price livel 
# Calculate Price Levels (P_t)
complete_filtered_data <- complete_filtered_data %>%
  group_by(REF_AREA) %>%
  mutate(Price_Level = nominal_GDP / real_GDP)

# Calculate Inflation Rates (π_t)
complete_filtered_data <- complete_filtered_data %>%
  arrange(REF_AREA, TIME_PERIOD) %>%
  mutate(Inflation_Rate = ((Price_Level - lag(Price_Level))/ lag(Price_Level))* 100)

# Print the resulting data frame
print(complete_filtered_data, n = 100)

#god its finally down, its time to save

write_xlsx(complete_filtered_data, "/Users/tie/Documents/GitHub/RA-data-clening/Data/IFS_cleaned_data.xlsx")
```

```

```{r}
#its the time to create check flie 
#extract the data duration for each country

data_duration <- raw_data %>%
  group_by(REF_AREA) %>%
  summarize(
    start_year = min(TIME_PERIOD, na.rm = TRUE),
    end_year = max(TIME_PERIOD, na.rm = TRUE)
  ) %>%
  mutate(data_duration = paste(start_year, "-", end_year))

```



```{r}

#find the country that have at least 25 year olf 
# 计算每个国家的年份数据并生成标识
years_count <- raw_data %>%
  filter(!is.na(nominal_GDP) & !is.na(real_GDP)) %>%
  group_by(REF_AREA) %>%
  summarize(years_of_data = n_distinct(TIME_PERIOD)) %>%
  ungroup()  # 解除分组

# 创建包含所有国家的完整列表
complete_country_list <- data.frame(REF_AREA = unique(raw_data$REF_AREA))

# 使用 left_join 保留所有国家，并将缺失年份数据设置为0
years_count_complete <- complete_country_list %>%
  left_join(years_count, by = "REF_AREA") %>%
  mutate(
    years_of_data = ifelse(is.na(years_of_data), 0, years_of_data),
    has_25_years = ifelse(years_of_data >= 25, "1", "0")
  )

print(n_distinct(years_count_complete$REF_AREA))  # 应该输出198
print(years_count_complete)
```


```{r}

#market the country that have in the final data set 
included_in_filtered <- complete_filtered_data %>%
  distinct(REF_AREA) %>%
  mutate(in_filtered_data = 1)

```


```{r}
# 1. 创建包含所有国家的完整列表，并与 years_count 合并
years_count_complete <- data.frame(REF_AREA = unique(raw_data$REF_AREA)) %>%
  left_join(years_count, by = "REF_AREA") %>%
  mutate(
    years_of_data = ifelse(is.na(years_of_data), 0, years_of_data),
    has_25_years = ifelse(years_of_data >= 25, "1", "0")
  )

# 2. 将 data_duration、years_count_complete 和 included_in_filtered 数据框进行合并
final_summary <- data_duration %>%
  left_join(years_count_complete, by = "REF_AREA") %>%
  left_join(included_in_filtered, by = "REF_AREA") %>%
  mutate(in_filtered_data = ifelse(is.na(in_filtered_data), 0, in_filtered_data))

# 打印结果以检查
print(final_summary)
```



```{r}

# 选择并排列所需的列
final_summary <- final_summary %>%
  select(
    country_code = REF_AREA,
    data_duration,
    has_25_years,
    in_filtered_data
  )

# its time for check
print(final_summary)

```


```{r}
#change the time 
#new name = the old name

final_summary <- final_summary %>%
  select(
    country_name = country_code,
    data_duration,
    has_25_years,
    In_IFS_dataset = in_filtered_data
  )


print(final_summary)
write.xlsx(final_summary, "/Users/tie/Documents/GitHub/RA-data-clening/Data/IFS_data/IFS_final_summary.xlsx")

```


```{r}
library(readxl)
the_OECD_ultra_check_list <- read_excel("~/Library/CloudStorage/OneDrive-CarletonUniversity/The GDP data cleaning-TIEMA/the OECD ultra check list.xlsx", 
    col_types = c("text", "skip", "skip", 
        "numeric"))

print(the_OECD_ultra_check_list)

#put everything together

IFS_final_ultra_check_list <- final_summary %>%
  left_join(the_OECD_ultra_check_list$, by = "country_name")

head(IFS_final_ultra_check_list)


```


























