---
title: "Markdown Tie Project"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```





#just for code practice and play around it
################################################################################

#clean the enviroment

```{r}
rm(list = ls())
```


#set the working direction
#setwd("/Users/tie/Documents/GitHub/RA-data-cleaning-work/Code practice")

#create a new file for the data 
#dir.create("/Users/tie/Documents/GitHub/RA-data-cleaning-work/Code practice", recursive = TRUE)


################################################################################
#Step one Lode the all package that necessary. 
#some of them may not be used this file
#I just copy them around, so it will make my life easier 
```{r}
library (lubridate)     #the time series processing package
library (cansim)        #provides easy access to the statistics canada data tale
library (WDI)           #Accesses data from the world development indicators
library (fredr)         #provide an interface to the federal reserve economic data API
library (tsbox)         #Make time series conversion, aggregation and plotting simple
library (RColorBrewer)  #color palettes for R graphics
library(wesanderson)    #Provides color palettes inspired by Wes Anderson films.
library(writexl)        #Writes data frames to Excel files.
library(tidyr)          #Tidies messy data   
library(xts)            #Extensible time series class for R   
library(dplyr)          #Data manipulation and transformation.
library(openxlsx)       #Read, write, and edit Excel files.
library(knitr)
library(testthat)
install.packages("ggplot2")
library(ggplot2)

#Note: OECD change their API tool make the default download OECD package will not work
#so I have to download from github

#For whoever read this after 2024/05/18 please check the the default download OECD package
#support the OECD new API or not


library(devtools)
install_github("expersso/OECD")

library(OECD)
#load the function
#source("C:\Users\Ezra\Desktop\Tei R code")
```

################################################################################
#API
################################################################################

```{r}
dataset <- "OECD.SDD.NAD,DSD_NAMAIN10@DF_TABLE1,1.0"

filter <- "A.AUT+BEL+CAN+CHL+COL+CRI+DNK+CZE+EST+FIN+FRA+DEU+GRC+ISL+HUN+ISR+IRL+JPN+KOR+ITA+USA+GBR+TUR+CHE+ESP+SVN+SWE+SVK+MEX+LVA+LTU+LUX+NLD+NZL+NOR+POL+PRT+ZMB+ZAF+SGP+SRB+SEN+RUS+SAU+MKD+ROU+MAR+MLT+IDN+MDG+HKG+IND+GEO+CYP+HRV+CHN+CMR+CPV+BGR+ARG+WXOECD+ALB+BRA+EU15+EA20+OECDE+OECD26+EU27_2020+OECD+AUS.S1..B1GQ....USD_PPP.LR+V..T0102"

raw_data <- get_dataset(dataset, filter)
```

################################################################################

```{r}
#check the data
unique_values <- raw_data %>% 
  summarise_all(~ list(unique(.)))

#create a new data frame for all useful data col
selection_data <- select(raw_data, TIME_PERIOD, UNIT_MEASURE, REF_AREA, ObsValue, PRICE_BASE)

# Convert observations from character to numeric
selection_data$ObsValue <- as.numeric(selection_data$ObsValue)

# Ensure TIME_PERIOD is numeric in the selection_data
selection_data$TIME_PERIOD <- as.numeric(selection_data$TIME_PERIOD)

# Define a complete range of years and countries
all_countries <- unique(selection_data$REF_AREA)

#create the sequence for from the smallest year to the largest year
all_years <- seq(min(selection_data$TIME_PERIOD, na.rm = TRUE), max(selection_data$TIME_PERIOD, na.rm = TRUE), by = 1)

# Create a full grid of TIME_PERIOD, REF_AREA, MEASURE, and UNIT_MEASURE
# Assuming all_years and all_countries are defined and unique
#all_years <- c(2021, 2022)  # Example values
#all_countries <- c("USA", "CAN")  # Example values

# Create full grid
full_grid <- expand.grid(
  TIME_PERIOD = all_years,
  REF_AREA = all_countries,
  PRICE_BASE = unique(selection_data$PRICE_BASE),
  UNIT_MEASURE = unique(selection_data$UNIT_MEASURE)
)

# Perform the left join
selection_data <- full_grid %>%
  left_join(selection_data, by = c("TIME_PERIOD", "UNIT_MEASURE", "REF_AREA", "PRICE_BASE"))

# Print the resulting data frame to verify the join
print(selection_data)

#pivot_wide the data 
wide_data <- selection_data %>%
  pivot_wider(
    names_from = c(PRICE_BASE),
    values_from = ObsValue,
    names_sep = "_"
  )
```

```{r}

# Count the number of years for each country with non-NA values for both L and LR
years_count <- wide_data %>%
  filter(!is.na(V) & !is.na(LR)) %>%
  group_by(REF_AREA) %>%
  summarize(years_of_data = n_distinct(TIME_PERIOD))


```


# Filter countries with at least 25 years of data

```{r}

countries_to_keep <- years_count %>%
  filter(years_of_data >= 25) %>%
  pull(REF_AREA)

```




# Filter the original test_data to keep only the selected countries

```{r}
wide_data %>%
  filter(REF_AREA %in% countries_to_keep)
```

```{r}

filtered_data <- wide_data %>%
  filter(REF_AREA %in% countries_to_keep)

```


# Check if every country has data for the entire time period from 1950 to 2023

```{r}
coverage_check <- filtered_data %>%
  group_by(REF_AREA) %>%
  summarize(complete_years = all(1950:2023 %in% TIME_PERIOD), .groups = 'drop')
```


# Print the coverage check
```{r}
print(coverage_check, n = 100)
```


```{r}
# Rename variables to match
filtered_data <- rename(filtered_data, nominal_GDP = V)
filtered_data <- rename(filtered_data, real_GDP = LR)

```

```{r}

# Calculate Price Levels (P_t)
filtered_data <- filtered_data %>%
  group_by(REF_AREA) %>%
  mutate(Price_Level = nominal_GDP / real_GDP)

# Calculate Inflation Rates (π_t)
filtered_data <- filtered_data %>%
  arrange(REF_AREA, TIME_PERIOD) %>%
  mutate(Inflation_Rate = (Price_Level - lag(Price_Level)) / lag(Price_Level) * 100)

# Print the resulting data frame
print(filtered_data, n = 100)


```

```{r}
# Make excel file

write.xlsx(filtered_data, file = "C:/Users/Ezra/Desktop/Tei R code/raw_data.xlsx")

```

